The Impact of Anthropogenic Forcing on ENSO Amplitude

### 2021-08-24 presentations/presentation/presentation.tex
presentation looks even better

  \tikzstyle{process}=[circle, draw=red!50,fill=red!20, line width = 0.3mm]
  \tikzstyle{data}=[rectangle, draw=lightblue!50,fill=lightblue!20, line width = 0.3mm]

@@

\begin{frame}{References}
  \bibliographystyle{apalike}
  \fontsize{5pt}{6}\selectfont
  \bibliography{references.bib}
\end{frame}

@@

>>>>

  \tikzstyle{process}=[circle, draw=process, fill=process!20, line width = 0.3mm]
  \tikzstyle{data}=[rectangle, draw=data, fill=data!20, line width = 0.3mm]

@@

\begin{frame}{References}
  \bibliographystyle{apalike}
  \fontsize{4pt}{5}\selectfont
  \bibliography{references.bib}
\end{frame}

@@

%hi
